\chapter*{Acknowledgments}


First, thank you to Stuart Littlefair. This thesis and the work that went into it has only been possible with your guidance and help.
Big thanks also go to the rest of the white dwarf group at Sheffield for lending their ears and knowledge over the years. You helped more than you know, but amongst other things thanks to Vik Dhillon and Dave Sahman for teaching me how to use telescopes, Martin Dyer for his sage wisdom and wonderful company, and Steven Parsons and Alex Brown for making the latter parts of this thesis possible at all.
Thank you to Paul Kerry, for setting the bar for good tech support to such an impossibly high level.
Finally, thank you to my wife, Charlotte. You know exactly what this work has meant to me, and the value of the love and support you've given me can't be understated.

I would like to acknowledge the Science and Technology Facilities Council (STFC) for providing the funding for my PhD, and the Isaac Newton Group (ING) of la Palma and the National Astronomical Research Institute of Thailand (NARIT) for the use of their telescopes in this work. A further thanks to the European Southern Observatory, for the opportunity to use their instruments to aid the work of others.

I can't forget to thank the fellow PhD students that have come and gone through the years, and given me such excellent company. In no particular order, thank you to Liam, Johnny, James, Christina, Emma, Lydia, Umar, Rebecca, Alex, Luke, George, and Summer, for all the good times.
To my family, thank you for all the time you've spent listening to me witter on about my research -- Mum and Dad, by brother Ted, my second parents in Mike and Angie, and Alex and Kathleen. Your patience and inexhaustible words of encouragement have been deeply helpful.